Infra-estrutura de Testes para Implementações de Referência do Standard ECMAScript

### 2022-05-24 paper.tex
first draft of design and methodology

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{hyperref}

@@

% Para1 --> problemas da metada existente na Metadata262 v0. 
% --> as versoes estao mal calculadas porque nao existem JS engines 
% que implementem exactamente uma versao e so essa versao 
% --> versoes calculadas em instalacoes ad-hoc 
% -- é preciso melhorar a analise dinamica considerando mais JS engines 
% --> os built-ins tb estao mal calculados porque a analise dinamica 
% dos built-ins ignora propriedades -> so considera chamadas a funcoes 
% por isso, se um teste for apenas: Array.prototype.pop = 3; 
% nao vai ser identificado como um teste que usa o array pela analise 
% dinamica 
% --> ha informacao em falta 
% ficheiros da harness e funcoes da harness
% data de criação do teste 
% Para 2 --> Problemas de acesso a metadata e obtencao de informacao estatistica 
% sobre os testes 
% --> neste momento quem quiser obter informacao estatisca sobre os 
% testes tem de interagir com uma base de dados Mongo e depois processar a informacao 
% como entender
% O objectivo desta tese é resolver estes dois problemas. 
% 5.1 - Precise Metadata for test262 tests 
% --> calcular a metadata precisamente e de forma facilmente reproducible 
% 5.1.1 versao -> 
% Montar um sistema escalavel para o calculo das versoes 
% associamos a cada versao um numero arbitrario de docker images cada uma 
% com um JS engine supostamente dessa versao 
% ---> parelelizacao etc
% 5.1.2 built-ins -> melhorar a instrumentcao para o calculo dinamico dos 
% built-ins --> em particular, apanhar property look-ups dinamicamente

@@

% OLD DEPRECATED
\paragraph{OLD DEPRECATED} \colorbox{orange}{Para rescrever tudo com a nova estrutura!}

%  grandes objectivos 
This thesis is a continuation of Miguel Tringo's master thesis, aiming to complete the calculation of the \texttt{Frontmatter} metadata especially the \colorbox{orange}{metadata about the \texttt{harness}}, also aims to improve the generated metadata. Another aim of this thesis is to create a website for visualizing the metadata generated. \colorbox{orange}{Finally,} we aim to build a platform that allows users to submit the markdown generated from executing the \texttt{Test262} and compare different runs.
% QUESTION campo features? (restantes talvez possam ser ignorados author, negative, flags, info and description)
% QUESTION incluir?

% - processamento completo da metadata oficial 
% -> o processamento do miguel esta incompleto -> nao incluir informacao informacao sobre -> ... 
% [pode criticar como entender]
Miguel Trigo's thesis metadata is incomplete in various ways, tests with unknown \texttt{version} around 9000, tests without \texttt{built-ins} around 17000, and tests without \texttt{syntactic\_construct} around 13000 \colorbox{orange}{tests without esid around 600}.
% QUESTION sao tests da versao seginte de ECMA que ainda nao tem seccao na versao actual?
%
The metadata from the thesis could be improved in way the data is arranged, for example, the subfolders of the path to the test are spread into the JSON Object of the test. The subfolders information being put into an array of ordered subfolders would increase the readability.

% - calculo mais preciso da nova metadata proposta
% - o calculo da versao pode ser melhorado de varias maneiras
This thesis plans to improve the \texttt{version} metadata generation in two dimensions precision and efficiency.
% - Precisao 
% - usar mais engines
For the precision, with more \texttt{JavaScript} engines being used, there would be more certainty when determining the version.
% - Eficiencia 
% - paralelizar os engines 
As for the efficiency, it would be possible to parallelize the waterfall model of the dynamic approach running multiple tests at the same time. It is also possible to use \texttt{git diff} to identify the tests that were added or changed since the last time the dynamic approach was executed, \colorbox{orange}{ only needing to execute} the dynamic approach on the differences.
% QUESTION e' problema se fizerem update noutro lado que afeta o teste indiretamente?

% - Sistema de visualisacao da metadata 
The website for visualizing the metadata aims to make access to the metadata and filtering it easily accessible. The website is planned to allow the search

% % printscreens do site 
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=1\textwidth]{images/website.png}
%     \caption{Website for searching the metadata in construction}
%     \label{fig:website}
% \end{figure}

@@

\paragraph{Concluding visualization system}
This task consists of concluding the \texttt{MetaData262 v0} visualization system by adding the possibility to view statistics about the queried tests and improving the system's reliability through preparing it to handle wrong queries.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{subcaption}

@@

In this section we will discuss the improvements this thesis will make to \texttt{MetaData262 v0} as well as the MetaData262 visualization system that will be created to improve ease of access to the MetaData262 information.

\subsection{Improvements to MetaData262 v0}
\label{sub:improvements_to_metadata262_v0}

% Para1 --> problemas do calculo da metada existente na Metadata262 v0. 
% --> as versoes estao mal calculadas porque nao existem JS engines 
% que implementem exactamente uma versao e so essa versao 
% --> versoes calculadas em instalacoes ad-hoc 
% -- é preciso melhorar a analise dinamica considerando mais JS engines 
% --> os built-ins tb estao mal calculados porque a analise dinamica 
% dos built-ins ignora propriedades -> so considera chamadas a funcoes 
% por isso, se um teste for apenas: Array.prototype.pop = 3; 
% nao vai ser identificado como um teste que usa o array pela analise 
% dinamica 
% --> ha informacao em falta 
% ficheiros da harness e funcoes da harness
% data de criação do teste 
The metadata calculated by \texttt{MetaData262 v0} is flawed several ways: in the version calculation, in the built-in calculation, and in the harness calculation. These flaws will described in more detail next.

\begin{itemize}
\item \emph{Version Calculation} - The version calculation is flawed in both the static and dynamic approach, meaning that the hybrid approach that uses the results of the previous two will also be compromised. The static approach is flawed since the \texttt{Esprima} parser only supports fully up until \texttt{ECMAScript} version 7. The solution to that is to find a JS parser that supports a later version of the standard. The dynamic approach's flaw lies in the way it works, since there is no JS engine that fully supports a version of the standard and only that one. To improve the dynamic approach we will add more JS engines.
%
\item \emph{Built-in Calculation} - The built-in calculation is also flawed in both the static and dynamic approach. The static approach has the same flaw since \texttt{Esprima} is the parser used. Therefore the same improvement can be made, finding a newer parser. As for the dynamic approach is is flawed due to the fact that only function calls are detected, if the properties of a built-in are change directly then it will not be detected. For example if the test preforms \texttt{Array.prototype.pop = 3;} then the property prototype of the Array built-in will be changed even though no function call was made and it will go undetected by the dynamic approach.
%
\item \emph{Harness Calculation} - The harness calculation very flawed containing only the little information available in the \texttt{Frontmatter} of a few tests. This calculation can be improved by completing \texttt{includes} metadata and adding the \texttt{harness-functions} metadata. Both are mentioned in earlier sections, the \texttt{includes} stores the files of the \texttt{harness} needed to run the test and the \texttt{harness-functions} will store the functions from those files that are actually used.
\end{itemize}

% Para 2 --> Scalability/Performance and Replicability of the calculation
% 5.1 - Precise Metadata for test262 tests 
% --> calcular a metadata precisamente e de forma facilmente reproducible 
% 5.1.1 versao -> 
% Montar um sistema escalavel para o calculo das versoes 
% associamos a cada versao um numero arbitrario de docker images cada uma 
% com um JS engine supostamente dessa versao 
% ---> parelelizacao etc
% 5.1.2 built-ins -> melhorar a instrumentcao para o calculo dinamico dos 
% built-ins --> em particular, apanhar property look-ups dinamicamente
Improving the calculations of the \texttt{MetaData} will enhance the issue of performance, we will improve the performance with the use of \texttt{docker}\cite{docker} containers and this way we will also improve the ease to replicate the calculations. The duration to calculate the version with the dynamic approach scales linearly with the amount of engines per standard version being used. In \texttt{MetaData262 v0} only two JS engines are being used and the dynamic approach duration takes multiple hours to run. With the use of \texttt{docker} containers we will be able to make the parallelize the work of the dynamic approaches through multiple docker images. Containers running in parallel will not only improve the performance but also allow MetaData262 to be replicated in an easier way since the is less requirements and the replication will be standardized.

\subsection{MetaData262 Visualization System}
\label{sub:metadata262_visualization_system}

% --> Problemas de acesso a metadata e obtencao de informacao estatistica 
% sobre os testes 
% --> neste momento quem quiser obter informacao estatisca sobre os 
% testes tem de interagir com uma base de dados Mongo e depois processar a informacao 
% como entender
% O objectivo desta tese é resolver estes dois problemas.

% Para 0 --> Motivar a criacao do system de visualizacao
The \texttt{MetaData262 Visualization System} appears to ease the barrier to access the \texttt{MetaData262 v0} information and statistics. Right now the metadata is hosted in a MongoDB database leading to the need to have knowledge of MongoDB to get the information. After getting the information there would most likely be a need to process that data and maybe even generating charts to provide statistics of the data. This is visualization system will make this process much easier.

@@

% Para 1 --> O que o website vai mostrar e o que para isso e' necessario fazer
The \texttt{MetaData262 Visualization System} is in its core a web application that allows users visualize the metadata calculated easily and updates it self whenever there are changes in \texttt{Test 262}. Users are will to filter the metadata for the built-ins and version of the test. Users will also be able visualize the queried information in different ways: \texttt{PATH}, \texttt{JSON}, and \texttt{STATS}. The \texttt{PATH} will only show the path to the tests in \texttt{Test262}. The \texttt{JSON} will allow the users to see the full metadata calculated for the tests. Finally, the \texttt{STATS} will show some statistics about the tests queried. To ensure that the information is up to date this system needs to update it self since this is a thesis project and there is no active developer team. In order to accomplish that, the system will need check for changes, be it in the form of new tests or changes to existing ones, and calculate the new metadata.

% Para 2 --> O que ja esta feito
The development of the web application has already began, in \colorbox{orange}{Figure} \ref{fig:website} it is possible to see the progress already made. The image has 2 main parts: the filters part, and the information part.
%
The upper part is the filters part, where it is possible to select the filters for querying the metadata. The first filter, \texttt{BuiltIn Belongs} allows to select tests from the subfolders of the built-in folder in the \texttt{Test262}. The \texttt{BuiltIn Contained} enables the user to filter tests by the built-ins the tests can use. The \texttt{BuiltIn Belongs} and \texttt{BuiltIn Contained} filters are combined using \texttt{AND} or \texttt{OR} relations. The \texttt{AND} relation will only return tests that satisfy both filters. As for the \texttt{OR} relation it will return every test that satisfies either of the filters. After we have the \texttt{Version} filter that allows filtering the tests by the \texttt{ECMAScript} version. Next we have the \texttt{BACKEND SEARCH} and \texttt{LOCAL SEARCH} search buttons that will query the metadata database for the tests that satisfy the filters set. The \texttt{BACKEND SEARCH} filter the tests in the backend server while the \texttt{LOCAL SEARCH} it will filter the tests in the machine that is used to access the website.
%
In the example the filters selected are \texttt{Object}  and \texttt{Array} for the \texttt{BuiltIn Belong} and \texttt{BuiltIn Contained} respectively with an \texttt{AND} relation and the sixth version is also selected.
%
Finally, the information part of the image contains the result of the query. The information can already be displayed in two of the three ways mentioned above, in the image the \texttt{PATH} is selected. Afterwards the image shows it took 16 milliseconds to have the query results available to the user. Next the image displays that a total of 32 tests satisfy the filters selected. Finally, the image shows the path of the tests tests selected. Note that not all tests are shown at the same time, in order to improve performance only 10 tests are shown at a time, at the bottom of the image is the pagination menu.
% QUESTION mudar o titulo do website para MetaData262 Visualization System ??

% printscreens do site 
\begin{figure}[ht]
    \centering
    \includegraphics[width=1\textwidth]{images/website.png}
    \caption{Website for searching the metadata in construction}
    \label{fig:website}
\end{figure}

% Para 3 --> Trade off the fazer a filtragem local or no servidor
In Figure \ref{fig:website} there are two search buttons because there at the time trade offs being made with either way of searching, the following results were run in the laptop serving the web application. The backend search starts getting slow whenever the amount of tests being returned surpasses 2500 in the local machine, taking on roughly half a second to get the results. The local search has the problem that it takes around 4 seconds to get all the metadata from the server at page load. The local search has the advantage of filtering the tests in a few milliseconds. Caching the metadata in the users browser would allow the metadata to be only loaded one, making the usability of the web application much better.

% Para 4 --> Os graficos que queremos gerar --> bibliotecas
This web application will allow the user to view charts about the metadata of the tests queried. M. Trigo's thesis he generated the charts shown in Figure \ref{fig:grafico_bigodes} and Figure \ref{fig:grafico_stackBar} as well as some other pie charts and bar charts. In the web application those charts will be generated in real time with the help of external libraries. Especially the charts below, the box and whiskers chart and the stacked bar chart, are not supported by many of the most popular libraries. Two of the libraries that are capable of generating all the charts needed are the \texttt{KendoReact}\cite{KendoReact} an UI library and \texttt{Victory}\cite{Victory} a chart library. \texttt{KendoReact} is a full UI library, charts being only part of its 126 components. Whereas, the \texttt{Victory} library has only 34 components and all are directly related with generating charts. The Victory library also seams simpler to use, the community around it seams more active which would be important in case of difficulty while implementing the charts needed.

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=0.95\textwidth]{images/n_asserts.png}
  \captionof{figure}{M. Trigo chart number of asserts by category}
  \label{fig:grafico_bigodes}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=0.95\textwidth]{images/version.png}
  \captionof{figure}{M. Trigo chart versions by category}
  \label{fig:grafico_stackBar}
\end{minipage}
\end{figure}

% Para 5 --> breve descricao do processo para manter a metadata atualizada
% ignorado por estar com 3 paginas so' sobre o website

@@

\paragraph{Concluding visualization system}
This task consists of concluding \texttt{MetaData262 v0} visualization system by adding the possibility to view statistics about the queried tests and improving the system's reliability through preparing it to handle wrong queries.
